---
title: "Homework3"
author: "Monica Vermillion"
date: "February 16, 2019"
output:
  pdf_document: default
  html_document: default
---
## Question 1: Effect of Cut on the Price of Diamonds 

```{r setup, include=FALSE}
setwd("H:/HierarchicalModel/Homework/homework3_vermillion")
```
Load the Data:
```{r Load Data Boxplot and P Estimates}
# Quesiton 1: What is the effect of cut on the price on a diamond?
diamonds <- read.csv("diamond.csv") # load diamond data 
head(diamonds)# see fist 6 of data 
#Order of Cuts: Fair, Good, Very Good, Premium, Ideal  
boxplot(price~cut,data = diamonds, col="lightgray", notch = TRUE) # create boxplot 
dim <- glm(price~cut, data = diamonds, family = "poisson") # fit data to a poisson distribution 
d_coef <- coef(dim) #extract the coeffcients/ parameter estimates? 
```


```{r Effect Claculations}
#Effect SIze between two values of X: exp(a+b*x2)-exp(a+b*x1) *exp() is the link func for poisson
#Intercept/ Baseline for a fair cut 
exp(d_coef[1])
inter <- exp(d_coef[1])
#Effect size Good Cut 
exp(d_coef[1]+d_coef[2])-inter
#Effect size of a Very Good Cut (coef6)
exp(d_coef[1]+d_coef[3])-inter
#Effect size of a Premium Cut 
exp(d_coef[1]+d_coef[4])-inter
#Effect size of an ideal cut 
exp(d_coef[1]+d_coef[5])-inter

```
### Effect of Each Type of Cut 

The baseline for a fair cut diamond is $4358.75, this comes from the inital intercept values connected through a log link. A good cut on a diamond decreases the price genreally by $429.89. A very good cut on a diamond also generally decreases the price from the baseline by $901.21. A premium cut effects the baseline price by generally increasing the price by $225.50. An ideal cut on a diamond effects the baseline by generally decreasing the price by $376.99. 
Conclusion: Diamonds are really expesnive and getting a very good cut 

``` {r 95% CI}
exp(confint(dim))

```
All of the confidence intervals are extremely small and they are all positive (don't cross 0), indicating a strong confidence in the relationship of cut and price. 

## Question 2: Imact of Eduction on Contraceptive Use 

``` {r Question 2}
cuse <- read.csv("contraception.csv")
head(cuse)
```

```{r Binomial Distribution}
# Use Bionomial Distribution, data is proportional 
response <- cbind(cuse$notUsing, cuse$total-cuse$notUsing) #proportional response 
boxplot(response~cuse$education) #boxplot of the data 
B_cuse <- glm(response~education, data=cuse, family = "binomial") #model fit to bionomial 
coef(B_cuse)
plogis(coef(B_cuse)) #on real number line 
confint(B_cuse)
plogis(confint(B_cuse))
```
## Question 3: HERricanes vs HIMmicanes

```{r Question 3}

hurricanes <- read.csv("Hurricane Dataset.csv")
head(hurricanes)

FemHer <- glm(alldeaths~Gender_MF, data = hurricanes, family = "poisson")
boxplot(alldeaths~Gender_MF, data=hurricanes)
coef(FemHer)
exp(coef(FemHer))
confint(FemHer)


```
From the poisson  distribution the "sex" of the hurricane is a good indicator of the death count. 

## Question 4: My Own Data 

```{r Question 4}
plant <-  read.csv("Copy of Vegetation_Plot_PercentAreaCover_2018.csv")
plant$ï..Plot.Number <- NULL
head(plant)
boxplot(plant)
#Percent Area Cover so use Beta distribution 
Beta_plant <- 
```




